Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-07-19 paper.tex
conclusion added

Things to address

\begin{itemize}
\item
  demand for tutorials exceeded expectations
\item
  tutorials helpful in understanding ABM
\item
  international cooperation
\item
  Digital competency framework / Skills passport
\item
  OER: open learning
\item
  Future aspects:

  \begin{itemize}
  \item
    application in educational programmes
  \item
    community driven updates (?)
  \end{itemize}
\end{itemize}

>>>>

The process of creating and testing Open Educational Resources for Agent-Based Modelling for Archaeologists showed us many things. The demand for tutorials exceeded our expectations, showing the importance of creating these materials. The testing of tutorials during workshops at international conferences proved very useful in gaining direct feedback. This greatly helped improving the material. The tutorials have proven their use in guiding learners into understanding ABM in an archaeological context. The international cooperation improved the quality of the material and also the accessibility of the material for various audiences. The integration in the Digital competency framework and Skills passport increased the didactic and pedagogic quality even while the latter is not yet published.

Future aspects of these open learning materials will be the further application and integration within the educational programmes in our universities and hopefully in others too. We have made the material openly available and we hope that the ABM-community will stay involved and that future updates will be community driven.
